---
title: "Data Collection and Analysis"
output: html_notebook
---

```{r setup}
library(tidyverse)
library(rvest)
library(pdftools)
library(quanteda)
```

# Creating Miscellaneous Dataframes

```{r state_abbrs}
# Equaldex and MAP data have data on more than the 50 states, so this will be used to filter and cross-reference state name and abbreviations.
States <- tibble(State = state.name, State.Abbr = state.abb)
States
```

# Web Scraping / Data Collection

## Table Scraping and Manipulation

### Equaldex

Information about Equaldex and link to site here

```{r equaldex_scrape}
Equaldex_url <- read_html("https://www.equaldex.com/equality-index/united-states")

# extracting the raw data
Equaldex_raw <- Equaldex_url %>% 
  html_element(xpath ='//*[@id="content"]/div[3]/table') %>% 
  html_table()
```


```{r equaldex_manipulation}
# extracting and manipulating the data
# index is on a scale out of 100
Equaldex_df <- Equaldex_url %>% 
  html_element(xpath ='//*[@id="content"]/div[3]/table') %>% 
  html_table() %>% 
  # separating column data
  separate('State and Territory', into = c('Rank', 'State'), sep = "\\. ", convert = T) %>% 
  separate('Equality Index', into = c('Equality_Index', 'Max1'), convert = T) %>% 
  separate('Legal Index', into = c('Legal_Index', 'Max2'), convert = T) %>% 
  separate('Public Opinion Index', into = c('Public_Opinion_Index', 'Max3'), convert = T) %>% 
  #removing unnecessary columns 
  select(-c(Max1, Max2, Max3)) %>%  
  #making average colummn to compare to MAP data
  mutate('Total_Index'= (Equality_Index + Legal_Index + Public_Opinion_Index) / 3) %>% 
  semi_join(States, by = 'State')

Equaldex_df
```

### MAP

Information about MAP and link to site here

```{r MAP_scrape}
MAP_url <- read_html("https://www.lgbtmap.org/equality-maps")

# extracting the raw data
MAP_raw <- MAP_url %>% 
  html_element(xpath = '//*[@id="map-4"]/div/table') %>% 
  html_table()
```


```{r MAP_manipulation1}
# extracting and manipulating
MAP_df <- MAP_url %>% 
  html_element(xpath = '//*[@id="map-4"]/div/table') %>% 
  html_table(header = T) %>% # works to rename, how to make it proper titles, how to add missing titles?
  rename('Alpha_Rank' = 1, 'Measured_Category' = 3) %>%  #renaming empty columns
  select(-Alpha_Rank) %>% #removes unnecessary initial column that numbered state positions
  semi_join(States, by = 'State') %>% 
  #separating the score and the scale
  separate('Relationship andParental Recognition', into = c('Relationship_and_Parental_Recognition', 'Relationship_and_Parental_Recognition_Scale'), sep = '/', convert = T) %>% 
  separate('Non–Discrimination', into = c('Non-Discrimination', 'Non-Discrimination_Scale'), sep = '/', convert = T) %>% 
  separate('Religious Exemption Laws', into = c('Religious_Exemption_Laws', 'Religious_Exemption_Laws_Scale'), sep = '/', convert = T) %>% 
  separate('LGBT Youth', into = c('LGBT_Youth', 'LGBT_Youth_Scale'), sep = '/', convert = T) %>% 
  separate('Healthcare', into = c('Healthcare', 'Healthcare_Scale'), sep = '/', convert = T) %>% 
  separate('CriminalJustice', into = c('Criminal_Justice', 'Criminal_Justice_Scale'), sep = '/', convert = T) %>% 
  separate('IdentityDocuments', into = c('Identity_Documents', 'Identity_Documents_Scale'), sep = '/', convert = T) %>% 
  rename('Sexual_Orientation_Policy_Tally' = 'Sexual Orientation Policy Tally', 'Gender_Identity_Policy_Tally' = 'Gender Identity Policy Tally', 'Overall_Tally'= 'Overall Tally')
# not all states have current legislation, so i will eventually filter out those that do not have current legislation as there is no ling data to look at for them
```


```{r MAP_manipulation2}
# Pivoting wider to separate gender identity and sexual orientation and cleaning up columns.
# vector types are a mess in the columns
MAP_df <- MAP_df %>% 
  pivot_wider(names_from = Measured_Category, names_sep = "_", values_from = Relationship_and_Parental_Recognition:Identity_Documents_Scale) %>% 
  select(-c(Identity_Documents_SO, Identity_Documents_Scale_SO)) %>%  # removing unnecessary columns
  # rearrange columns
  relocate('State', 'Relationship_and_Parental_Recognition_GI', 'Relationship_and_Parental_Recognition_Scale_GI','Relationship_and_Parental_Recognition_SO', 'Relationship_and_Parental_Recognition_Scale_SO', 'Non-Discrimination_GI', 'Non-Discrimination_Scale_GI', 'Non-Discrimination_SO', 'Non-Discrimination_Scale_SO', 'Religious_Exemption_Laws_GI', 'Religious_Exemption_Laws_Scale_GI','Religious_Exemption_Laws_SO', 'Religious_Exemption_Laws_Scale_SO', 'LGBT_Youth_GI', 'LGBT_Youth_Scale_GI', 'LGBT_Youth_SO', 'LGBT_Youth_Scale_SO', 'Healthcare_GI', 'Healthcare_Scale_GI', 'Healthcare_SO', 'Healthcare_Scale_SO', 'Criminal_Justice_GI', 'Criminal_Justice_Scale_GI', 'Criminal_Justice_SO', 'Criminal_Justice_Scale_SO', 'Identity_Documents_GI', 'Identity_Documents_Scale_GI', ends_with('Tally'))
head(MAP_df)
```

### Comparing MAP and Equaldex

Statistical test run

Create a df that has state, MAP/Equaldex total score, (and pro/anti legislation count. - add this after importing billtrack info)

```{r correlation_test}
State_Ranks_df <- Equaldex_df %>% 
  select(State, Total_Index) %>% 
  left_join(MAP_df %>% select(State, Overall_Tally),
            "State")
cor(State_Ranks_df$Total_Index, State_Ranks_df$Overall_Tally) # there is a very high correlation when states are in the same order
```

## Saving Freedom websites - collected data via JavaScript

The Freedom for all American's website uses a widget for the law data I am looking for, so Dan created a JavaScript code that pulled all necessary information and saved it as separate CSV files.

Dan got a working JavaScript code to pull all the data into CSV files from the JS tables.

INSERT JavaScript CODE HERE

Read in file names to map and create tibble.

Get filepath to work universally

```{r loading_files}
# pro
pro_files <- list.files(path = 'data/State-Bill-csvs/Pro/', pattern = '.csv', full.names = T)

# anti
anti_files <- list.files(path = 'data/State-Bill-csvs/Anti/', pattern = '.csv', full.names = T)
```


map across the dfs?

```{r pro_laws_tibble}
pro_laws <- pro_files %>% 
  map_dfr(., read_csv, name_repair = 'universal') %>% 
  select(-c(Position)) %>% # drop position, it is a blank column
  rename('BillTrack.Link' = 'Link', 'State.Abbr' = 'State') %>%  # will be adding another bill link to this tibble, adding in state names too
  mutate('Action.Year' = str_extract(Action.Date, '\\d\\d\\d\\d$'), .after = 'Action.Date') %>% 
  mutate('Bill.Stance' = 'Pro', .after = BillTrack.Link)
head(pro_laws)
```


```{r anti_laws_tibble}
anti_laws <- anti_files %>% 
  map_dfr(., read_csv, name_repair = 'universal') %>% 
  select(-c(Position)) %>% # drop position, it is a blank column
  rename('BillTrack.Link' = 'Link', 'State.Abbr' = 'State') %>%  # will be adding another bill link to this tibble, adding in state names too
  mutate('Action.Year' = str_extract(Action.Date, '\\d\\d\\d\\d$'), .after = 'Action.Date')%>% 
  mutate('Bill.Stance' = 'Anti', .after = BillTrack.Link)
head(anti_laws)
```

Join them together and add full state name.

```{r all_laws_tibble}
all_laws <- full_join(anti_laws, pro_laws) %>% 
  left_join(States, by = 'State.Abbr') %>% 
  relocate(State, .after = State.Abbr)
head(all_laws)
```

## BillTrack

EDIT THE BILLTRACK STUFF, MAKE SURE TO MENTION THAT THEY NEED PERMISSION TO RUN THIS

```{r billtrack_urls}
# create a character vector of all urls to pull data from
billtrack_urls <- c(anti_laws$BillTrack.Link, pro_laws$BillTrack.Link)
```


It is too big to run as one, so I will chunk it up.

```{r billtrack_scrape}
billtrack_df1 <- tibble('BillTrack.Link' = billtrack_urls[1:95]) %>% 
  mutate('Bill.PDF' = BillTrack.Link %>% map(~ .x %>% 
                                          read_html() %>% 
                                          # the links to each state information is housed in a table
                                          html_elements('#docs-table a') %>% 
                                          # returns a character vector/list in each column
                                          html_attr('href'))) 

billtrack_df2 <- tibble('BillTrack.Link' = billtrack_urls[96:190]) %>% 
  mutate('Bill.PDF' = BillTrack.Link %>% map(~ .x %>% 
                                          read_html() %>% 
                                          html_elements('#docs-table a') %>% 
                                          html_attr('href')))

billtrack_df3 <- tibble('BillTrack.Link' = billtrack_urls[191:285]) %>% 
  mutate('Bill.PDF' = BillTrack.Link %>% map(~ .x %>% 
                                          read_html() %>% 
                                          html_elements('#docs-table a') %>% 
                                          html_attr('href')))
```



```{r}
# billtrack_urls[1] %>% 
# "https://www.billtrack50.com/billdetail/1302835" %>% 
"https://www.billtrack50.com/billdetail/1410619" %>% 
  read_html() %>% 
  # the links to each state information is housed in a table
  html_element('#docs-table') %>% 
  html_table() %>% 
  filter(startsWith(`Document Type`, "Bill"),
         endsWith(`Source Location`, "pdf")) %>% 
  # slice(1) %>%
  pull(`Source Location`)

tibble(BillTrack.Link = c("https://www.billtrack50.com/billdetail/1410619",
                          "https://www.billtrack50.com/billdetail/1302835",
                          "https://www.billtrack50.com/billdetail/1417722")) %>% 
  mutate(links = map(BillTrack.Link,
                              ~ .x %>% 
                                read_html() %>% 
                                # the links to each state information is housed in a table
                                html_element('#docs-table') %>% 
                                html_table() %>% 
                                filter(startsWith(`Document Type`, "Bill"),
                                       endsWith(`Source Location`, "pdf")) %>% 
                                # slice(1) %>%
                                pull(`Source Location`)
  ),
  num_links = map_int(links, length),
  first_link = map_chr(links, 1)
  )
```


Join them into 1 df:

```{r billtrack_tibble}
# creating one tibble
billtrack_df <- tibble('BillTrack.Link' = c(billtrack_df1$BillTrack.Link, billtrack_df2$BillTrack.Link, billtrack_df3$BillTrack.Link), 'State.Link' = c(billtrack_df1$Bill.PDF, billtrack_df2$Bill.PDF, billtrack_df3$Bill.PDF))
```

Unnest individual URLs, then filter for only PDFs.

```{r billtrack_tibble_manipulation}
billtrack_df <- billtrack_df %>% 
  # generates a row per URL
  unnest(cols = State.Link, keep_empty = T) %>% 
  # filter for only links that go to pdfs
  filter(grepl('.pdf', State.Link)) %>% 
  # some state URLs are listed twice, remove duplicates
  filter(!duplicated(State.Link))
head(billtrack_df)
```


```{r billtrack_tibble_to_csv}
# saving the tibble into a csv to avoid future scraping
billtrack_df %>% 
  write.csv('data/billtrackdf.csv', row.names = T)
if (!exists("billtrack_df")) {
  billtrack_df <- read.csv("data/billtrackdf.csv")
}
```


```{r state_pdf}
# combine links and state info...bare bones for now
state_pdf_df <- billtrack_df %>% 
  left_join(all_laws, by = 'BillTrack.Link') %>% 
  select(BillTrack.Link, Bill.Stance, State.Link, State)
head(state_pdf_df)
```

# Working with PDFs and Creating a Corpus

Instructions pulled from: https://data.library.virginia.edu/reading-pdf-files-into-r-for-text-mining/

```{r pdf_clean_function}
# create a function to extract and tidy up the pdfs
clean_pdf <- function(file) {
  file %>% 
    pdf_text() %>% 
    str_split("[\\r\\n]+") %>%
    # remove pagination
    flatten_chr() %>%  
    # trim leading white space
    str_trim() %>% 
    # remove inner white space
    str_squish() %>% 
    # remove line numbers
    str_remove("^\\d+ ")
}  
```

Once again this is too large to run at once, chunk it and try again. The process proved to be finnicky, so I chunked it small to be able to diagnose issues easier.

```{r}
##Put state_pdf_df rows into chunks of 50ish
state_pdf_df %>% 
  mutate(num = row_number(),
         chunk = (num+1) %/% 50 + 1,
         .before=1)
```



```{r pdf_gathering, eval=FALSE}
# running df through the extracting and cleaning function
state_text_df1 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[1:50], 'Bill.Stance' = state_pdf_df$Bill.Stance[1:50], 'State.Link' = state_pdf_df$State.Link[1:50], 'State' = state_pdf_df$State[1:50]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

# error >
state_text_df2 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[51:100], 'Bill.Stance' = state_pdf_df$Bill.Stance[51:100], 'State.Link' = state_pdf_df$State.Link[51:100], 'State' = state_pdf_df$State[51:100]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

# error >
state_text_df3 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[101:150], 'Bill.Stance' = state_pdf_df$Bill.Stance[101:150], 'State.Link' = state_pdf_df$State.Link[101:150], 'State' = state_pdf_df$State[101:150]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

state_text_df4 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[151:200], 'Bill.Stance' = state_pdf_df$Bill.Stance[151:200], 'State.Link' = state_pdf_df$State.Link[151:200], 'State' = state_pdf_df$State[151:200]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

state_text_df5 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[201:250], 'Bill.Stance' = state_pdf_df$Bill.Stance[201:250], 'State.Link' = state_pdf_df$State.Link[201:250], 'State' = state_pdf_df$State[201:250]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

# error >
state_text_df6 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[251:300], 'Bill.Stance' = state_pdf_df$Bill.Stance[251:300], 'State.Link' = state_pdf_df$State.Link[251:300], 'State' = state_pdf_df$State[251:300]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

# error >
state_text_df7 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[301:350], 'Bill.Stance' = state_pdf_df$Bill.Stance[301:350], 'State.Link' = state_pdf_df$State.Link[301:350], 'State' = state_pdf_df$State[301:350]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

state_text_df8 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[351:400], 'Bill.Stance' = state_pdf_df$Bill.Stance[351:400], 'State.Link' = state_pdf_df$State.Link[351:400], 'State' = state_pdf_df$State[351:400]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

state_text_df9 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[401:450], 'Bill.Stance' = state_pdf_df$Bill.Stance[401:450], 'State.Link' = state_pdf_df$State.Link[401:450], 'State' = state_pdf_df$State[401:450]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

state_text_df10 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[451:500], 'Bill.Stance' = state_pdf_df$Bill.Stance[451:500], 'State.Link' = state_pdf_df$State.Link[451:500], 'State' = state_pdf_df$State[451:500]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

state_text_df11 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[501:550], 'Bill.Stance' = state_pdf_df$Bill.Stance[501:550], 'State.Link' = state_pdf_df$State.Link[501:550], 'State' = state_pdf_df$State[501:550]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

# error >
state_text_df12 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[551:600], 'Bill.Stance' = state_pdf_df$Bill.Stance[551:600], 'State.Link' = state_pdf_df$State.Link[551:600], 'State' = state_pdf_df$State[551:600]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

state_text_df13 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[601:650], 'Bill.Stance' = state_pdf_df$Bill.Stance[601:650], 'State.Link' = state_pdf_df$State.Link[601:650], 'State' = state_pdf_df$State[601:650]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

# error >
state_text_df14 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[651:700], 'Bill.Stance' = state_pdf_df$Bill.Stance[651:700], 'State.Link' = state_pdf_df$State.Link[651:700], 'State' = state_pdf_df$State[651:700]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

# error >
state_text_df15 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[701:750], 'Bill.Stance' = state_pdf_df$Bill.Stance[701:750], 'State.Link' = state_pdf_df$State.Link[701:750], 'State' = state_pdf_df$State[701:750]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))

# error >
state_text_df16 <- tibble('BillTrack.Link' = state_pdf_df$BillTrack.Link[751:792], 'Bill.Stance' = state_pdf_df$Bill.Stance[751:792], 'State.Link' = state_pdf_df$State.Link[751:792], 'State' = state_pdf_df$State[751:792]) %>% 
  mutate('Bill.Text' = map(State.Link, clean_pdf))
```


```{r}
state_text_df1 %>% 
  filter(str_detect(map(Bill.Text, 1), "HAWAW"))
  slice_sample(n=20) %>% 
  pull(Bill.Text) %>% 
  str(vec.len=3)
```


```{r}
all_laws %>% 
  select(BillTrack.Link, Last.Action)
billtrack_df
```

```{r}
state_pdf_df %>% 
  filter(endsWith(State.Link, "pdf")) %>% 
  nrow()
state_pdf_df %>% 
  filter(endsWith(tolower(State.Link), "pdf")) %>% 
  nrow()
state_pdf_df %>% 
  filter(!endsWith(tolower(State.Link), "pdf")) %>% 
  pull(State.Link)
state_pdf_df %>% 
  filter(endsWith(tolower(State.Link), "pdf"),
         !endsWith(tolower(State.Link), ".pdf")) %>% 
  nrow()
state_pdf_df %>% 
  filter(endsWith(tolower(State.Link), "pdf"),
         !endsWith(tolower(State.Link), ".pdf")) %>% 
  count(State)
state_pdf_df %>% 
  filter(State=="Minnesota")
```

```{r}
state_pdf_df %>% 
  filter(endsWith(State.Link, ".pdf"),
         State=="Virginia")

state_pdf_df %>% 
  filter(endsWith(tolower(State.Link), "pdf"),
         State!="Virginia")
```



```{r}
state_pdf_df %>% 
  filter(BillTrack.Link=="https://www.billtrack50.com/billdetail/1417722") %>% 
  pull(State.Link)
state_pdf_df %>% 
  filter(BillTrack.Link=="https://www.billtrack50.com/billdetail/1417722") %>% 
  mutate(Bill.Text = map(State.Link, clean_pdf))
```


```{r}
state_pdf_df %>% 
  filter(duplicated(BillTrack.Link))
state_pdf_df %>% 
  count(BillTrack.Link, sort=TRUE) %>% 
  count(n, name="nn")
state_pdf_df %>% 
  group_by(BillTrack.Link) %>% 
  filter(n()==4) %>% 
  relocate(State, .before=1)
```



```{r}
state_pdf_df %>% 
  filter(State=="Hawaii")
```


```{r statebill_tibble, eval=FALSE}
# creating one tibble
state_text_df <- tibble('BillTrack.Link' = c(state_text_df1$BillTrack.Link, state_text_df2$BillTrack.Link, state_text_df3$BillTrack.Link, state_text_df4$BillTrack.Link, state_text_df5$BillTrack.Link, state_text_df6$BillTrack.Link, state_text_df7$BillTrack.Link, state_text_df8$BillTrack.Link, state_text_df9$BillTrack.Link, state_text_df10$BillTrack.Link, state_text_df11$BillTrack.Link, state_text_df12$BillTrack.Link, state_text_df13$BillTrack.Link, state_text_df14$BillTrack.Link, state_text_df15$BillTrack.Link, state_text_df16$BillTrack.Link), 
                        'Bill.Stance' = c(state_text_df1$Bill.Stance, state_text_df2$Bill.Stance, state_text_df3$Bill.Stance, state_text_df4$Bill.Stance, state_text_df5$Bill.Stance, state_text_df6$Bill.Stance, state_text_df7$Bill.Stance, state_text_df8$Bill.Stance, state_text_df9$Bill.Stance, state_text_df10$Bill.Stance, state_text_df11$Bill.Stance, state_text_df12$Bill.Stance, state_text_df13$Bill.Stance, state_text_df14$Bill.Stance, state_text_df15$Bill.Stance, state_text_df16$Bill.Stance), 
                        'State.Link' = c(state_text_df1$State.Link, state_text_df2$State.Link, state_text_df3$State.Link, state_text_df4$State.Link, state_text_df5$State.Link, state_text_df6$State.Link, state_text_df7$State.Link, state_text_df8$State.Link, state_text_df9$State.Link, state_text_df10$State.Link, state_text_df11$State.Link, state_text_df12$State.Link, state_text_df13$State.Link, state_text_df14$State.Link, state_text_df15$State.Link, state_text_df16$State.Link), 
                        'State' = c(state_text_df1$State, state_text_df2$State, state_text_df3$State, state_text_df4$State, state_text_df5$State, state_text_df6$State, state_text_df7$State, state_text_df8$State, state_text_df9$State, state_text_df10$State, state_text_df11$State, state_text_df12$State, state_text_df13$State, state_text_df14$State, state_text_df15$State, state_text_df16$State), 
                        'Bill.Text' = c(state_text_df1$Bill.Text, state_text_df2$Bill.Text, state_text_df3$Bill.Text, state_text_df4$Bill.Text, state_text_df5$Bill.Text, state_text_df6$Bill.Text, state_text_df7$Bill.Text, state_text_df8$Bill.Text, state_text_df9$Bill.Text, state_text_df10$Bill.Text, state_text_df11$Bill.Text, state_text_df12$Bill.Text, state_text_df13$Bill.Text, state_text_df14$Bill.Text, state_text_df15$Bill.Text, state_text_df16$Bill.Text))
```


```{r state_text_tibble_to_csv, eval=FALSE}
# saving the tibble into a csv to avoid future scraping
billtrack_df %>% 
  write.csv('data/statetextdf.csv', row.names = T)
```
